\documentclass{article}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\title{Working notes}
\date{2020-04-21}
\author{jingmao you}
\begin{document}
 \pagenumbering{gobble}
 \maketitle
 \newpage
 \pagenumbering{arabic}

 \section{Whe storage of information }
All the information is extracted from jCas. 
\newline
After the KNOWNER pipeline, there will be named entities as the output. 

\section{What to do next}
The goal is to insert an jCas object, in order to run the aida analysis engine. 
\newline
This object should contain the same type of output as KNOWNER pipeline. 
\newline
Build a new pipeline, containing only Aida pipeline.
The input should be named enetities, which contains all the information that we need.

\section{How to build named entities?}
In order to see the named entities, I take a lood at the KnowNERIntegrationTest: \href{https://github.com/ambiverse-nlu/ambiverse-nlu/blob/341dc62abf47396aa04e6d0ca7c9e071b5d5b06e/src/main/java/de/mpg/mpi_inf/ambiversenlu/nlu/ner/KnowNERIntegrationTest.java}{KnowNERIntegrationTest}
\newline
From the testing file, it builds the document first, then it pass it to documentprocessor.
Document processor will process the document, and build the jCas instance.
The named entites could be extracted from the jCas.

\section{The document processor}
\begin{itemize}
	\item create jCas using JCasFactory
	\item addSettings to jCas
	\item set the document into jCas
    \item process jCas 
\end{itemize}


\section{The related links}
\begin{itemize}
  \item \href{https://uima.apache.org/d/uimaj-current/apidocs/org/apache/uima/jcas/JCas.html}{JCas}
  \item \href{https://github.com/ambiverse-nlu/ambiverse-nlu/blob/341dc62abf47396aa04e6d0ca7c9e071b5d5b06e/src/main/java/de/mpg/mpi_inf/ambiversenlu/nlu/entitylinking/processor/DocumentProcessor.java}{DocumentProcessor}
  \item \href{https://github.com/ambiverse-nlu/ambiverse-nlu/blob/341dc62abf47396aa04e6d0ca7c9e071b5d5b06e/src/main/java/de/mpg/mpi_inf/ambiversenlu/nlu/ner/KnowNER.java}{KNOWNER}
  \item \href{https://github.com/ambiverse-nlu/ambiverse-nlu/blob/341dc62abf47396aa04e6d0ca7c9e071b5d5b06e/src/main/java/de/mpg/mpi_inf/ambiversenlu/nlu/entitylinking/uima/pipelines/DisambiguationPipeline.java}{Disambiguation testing code}
\end{itemize}


\end{document}
